SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-27 paper.tex
minor changes

\textcolor{blue}{\textbf{(RP5)} provide tools and approaches capable of addressing different software languages and application interfaces, with the goal of reducing the time needed to adapt current verification techniques to new developments and technologies.}

@@

\textcolor{blue}{\textbf{(RP5)} Although ESMBMC \cite{Cordeiro12} was extended to support C/C++ and some variants, new application interfaces and languages are often developed, which then claim for suitable verification tools. Indeed, it would be interesting if one needed only to load a new language model, which along with a BMC core could check different programs. Some work towards that was already presented by Sousa, Cordeiro, and Filho, which employed operational models for checking Qt-based programs. In summary, the BMC core (in that case, ESBMC) is not changed, but instead an operation model, which implements the behavior and features of Qt libraries, is used for providing the new code structure to be checked. Such research problem is closely related to the first one \textbf{(RP1)} and has the potential to devise a new paradigm in software verification.}

@@

Given that software complexity has significantly increased in embedded products, there are still some (recent) advances to stress and exhaustively cover the system state space, in order to verify low-level properties that have to meet the application's deadline, access memory regions, handle concurrency, and control hardware registers. Besides, there is a trend towards incorporating knowledge about the system to be verified, which may take software verification one step further, where not only code correctness will be addressed, but also full system reliability. \textcolor{blue}{Finally, it seems interesting to provide behavioral models when new application interfaces or language features are used, in order to extend the capabilities of current verification tools, without changing the core BMC module.}

@@

%51
\bibitem{BeyerW15}
Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.

%52
\bibitem{RochaIFM12}
Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.

>>>>

\textbf{(RP5)} provide tools and approaches capable of addressing different programming languages and application interfaces, with the goal of reducing the time needed to adapt current verification techniques to new developments and technologies.

@@

{\textbf{(RP5)} Although ESBMC \cite{Cordeiro12} was extended to support C/C++ and some variants, new application interfaces and programming languages are often developed, which require suitable software verification tools. Indeed, it would be interesting if a new programming language model could be loaded, which along with a BMC core could check different programs. Some work towards that was already presented by Sousa, Cordeiro, and Filho~\cite{Garcia16}, which employed operational models for checking Qt-based programs from consumer electronics. In summary, the BMC core (in that case, ESBMC) is not changed, but instead an operational model, which implements the behavior and features of Qt libraries, is used for providing the new code structure to be checked. Such research problem is closely related to the first one \textbf{(RP1)} and has the potential to devise a new paradigm in software verification.

@@

Given that software complexity has significantly increased in embedded products, there are still some (recent) advances to stress and exhaustively cover the system state space, in order to verify low-level properties that have to meet the application's deadline, access memory regions, handle concurrency, and control hardware registers. Besides, there is a trend towards incorporating knowledge about the system to be verified, which may take software verification one step further, where not only code correctness will be addressed, but also full system reliability. Finally, it seems interesting to provide behavioral models when new application interfaces or programming language features are used, in order to extend the capabilities of current verification tools, without changing the core BMC module.

@@

%51
\bibitem{Garcia16}
Garcia M. , Sousa F., Cordeiro, L., Lima Filho E.: 
\newblock {\em{ ESBMC$^{QtOM}$: A Bounded Model Checking Tool to Verify Qt Applications}}. 
\newblock In: International SPIN symposium on Model Checking of Software (to appear), 2016.

%52
\bibitem{BeyerW15}
Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.

%53
\bibitem{RochaIFM12}
Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.
